taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-08-28 paper/manuscript.Rmd
add some details to the intro + darwin core citation

Instead of binding existing web APIs, `taxadb` is built around a set of compressed text files following a consistent, standardized layout or schema (discussed below). These files are automatically downloaded and imported and stored on a local database by `taxadb`.  The largest of the taxonomic naming providers today contain under 6 million name records with uncompressed file sizes under a GB, and can be compressed to around 50 MB and downloaded in under a minute on a 1 MB/s connection.  In contrast, querying a single name over the web API, requiring the server to respond, execute the query, and serialize the response, can take several seconds. Thus it does not take many taxa before transferring the entire data set to query locally is more efficient.  Moreover, this local copy can be cached on the user's machine, requiring only the one-time setup and enabling offline use.

@@

* software design - faster access, reproducible queries
* Darwin Core schema citation

>>>>

Instead of binding existing web APIs, `taxadb` is built around a set of compressed text files following a consistent, standardized layout or schema following the Darwin Core Standard [@Wieczorek2012]. These files are automatically downloaded and imported and stored on a local database by `taxadb`.  The largest of the taxonomic naming providers today contain under 6 million name records with uncompressed file sizes under a GB, and can be compressed to around 50 MB and downloaded in under a minute on a 1 MB/s connection.  In contrast, querying a single name over the web API, requiring the server to respond, execute the query, and serialize the response, can take several seconds. Thus it does not take many taxa before transferring the entire data set to query locally is more efficient.  Moreover, this local copy can be cached on the user's machine, requiring only the one-time setup, and enabling offline use and reproducible queries.

@@
